Supplemental Materials, Methods and Results

### 2022-04-21 supp/Supplemental Materials and Methods.Rmd
Realised that in long format we also need to make sure that V for each effect size is size by side in a single column. A few ways this can be done but probably most easily understood by ifelse

        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()

>>>>

        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43), values_to = "effect_size", values_drop_na = FALSE) %>% 
                    mutate(V = ifelse(name == "lnRR_Q10_acute_t1", V_lnRR_Q10_acute_t1, 
                                  ifelse(name == "lnRR_Q10_acute_t2", V_lnRR_Q10_acute_t2, 
                                  ifelse(name == "lnRR_Q10_acclim", V_lnRR_Q10_acclim, 
                                  ifelse(name == "lnVR_Q10_acute_t1", V_lnVR_Q10_acute_t1, 
                                  ifelse(name == "lnVR_Q10_acute_t2", V_lnVR_Q10_acute_t1, 
                                  ifelse(name == "lnVR_Q10_acclim", V_lnVR_Q10_acclim, 
                                  ifelse(name == "lnCVR_Q10_acute_t1", V_lnCVR_Q10_acute_t1, 
                                  ifelse(name == "lnCVR_Q10_acute_t2", V_lnCVR_Q10_acute_t2,V_lnCVR_Q10_acclim)))))))),
                           type = ifelse(grepl("acute", name), "acute", "acclim"),
                           obs = 1:n()) %>% dplyr::select(!grep("V_", colnames(.))) %>% data.frame()
